Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-08-03 writeup/conStruct.tex
new poplar figs, fixed eqn.1

\begin{equation}
\widehat{\Omega}_{i,j} = 
	\begin{cases}
		\frac{1}{L}
		\sum\limits_{\ell=1}^{L}{\left[ 	\left(f_{i,\ell} - \bar{f}_{\ell} \right)
		 	\left(f_{j,\ell} - \bar{f}_{\ell} \right)\right]
			} & \text{for } i \neq j \\
		\text{Var}_L\left( \text{B}(1,f_{i,\ell})	\right) & \text{for } i = j \\
	\end{cases}
\label{sample_covariance}
\end{equation}
\gb{ideas for how to describe what I'm doing on the diagonal in actual math notation?}

@@

}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_sp_clst_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=2$ through 7.
	Colors are consistent with Fig \ref{populus_sp_pies}.
    }\label{populus_sp_clst_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_nsp_clst_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the nonspatial \texttt{conStruct} model run with $K=2$ through 7.
	Colors are consistent with Fig \ref{populus_nsp_pies}.
    }\label{populus_nsp_clst_covs}
\end{figure}

>>>>

\begin{equation}
\widehat{\Omega}_{i,j} = 
	\begin{cases}
		\frac{1}{L-1}
		\sum\limits_{\ell=1}^{L}{\left[ 	\left(f_{i,\ell} - \bar{f}_{i} \right)
		 	\left(f_{j,\ell} - \bar{f}_{j} \right)\right]
			} & \text{for } i \neq j \\
		\bar{f}_i (1-\bar{f}_i) & \text{for } i = j \\
	\end{cases}
\label{sample_covariance}
\end{equation}

@@

} 
\gb{support for the spatial model over the nonspatial model at a given value of $K$ 
indicates that isolation-by-distance is likely a feature of the data at that level.}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_sp_clst_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=2$ through 7.
	Line colors are consistent with Fig \ref{populus_sp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \textit{P. balsamifera} and \textit{P. trichocarpa};
	green on green points are sample covariances between \textit{P. trichocarpa} and \textit{P. trichocarpa}.
    }\label{populus_sp_clst_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_nsp_clst_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the nonspatial \texttt{conStruct} model run with $K=2$ through 7.
	Line colors are consistent with Fig \ref{populus_nsp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \textit{P. balsamifera} and \textit{P. trichocarpa};
	green on green points are sample covariances between \textit{P. trichocarpa} and \textit{P. trichocarpa}.
    }\label{populus_nsp_clst_covs}
\end{figure}
